---
title: "IDEEL SRA Download"
author: "Nick Brazeau"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---
  
```{r setup, include=F, echo=F}
knitr::opts_chunk$set(echo = TRUE)
#####################################################
#################      Imports      #################
#####################################################

#Data Wrangling
library(tidyverse)
library(DT)
# SRA Downloading
library(rentrez)
library(SRAdb)
library(XML)
```

# SRA Downloads
We want to download the whole genome sequences from the following projects. 
  1. [MalaraiGen Pf3K](https://www.malariagen.net/apps/pf3k/release_3/index.html)
  2. [MalaraiGen Pf3K Mixtures](ftp://ngs.sanger.ac.uk/production/pf3k/release_5/pf3k_release_5_mixtures_metadata.txt)
  2. [MalaraiGen Pf Community Project](https://www.malariagen.net/projects/p-falciparum-community-project)
  2. [MalaraiGen Pf Genetic Crosses](https://www.malariagen.net/apps/pf-crosses/1.0/#samples)
  2. [MalaraiGen Vivax Genome Variation, Pearson et al. 2016](https://www.malariagen.net/apps/pvgv/index.html)
  2. [Hupalo et al. 2016 Vivax Genomic Variation](http://www.nature.com/ng/journal/v48/n8/abs/ng.3588.html?foxtrotcallback=true)


## MalariaGen Pf3K
This project has two components that are useful for us: samples (not yet finished) and the mixtures. For the samples, there are repeated samples names that looks like they were resequenced (i.e. PT0038-C and PT0038-Cx) but have the same ERS accession number. Will need to combine these using the R package `SRAdb`. **Below, I am going to read in their data file. This was downloaded from [Pf3K data browser](https://www.malariagen.net/apps/pf3k/release_3/index.html) on September 1, 2017. _This will  need to be updated with new data releases_**.









```{r}
setwd("~/Documents/MountPoints/mountIDEEL/Seq_Reads/")

# Following the SRADB manual found here: http://bioconductor.org/packages/release/bioc/vignettes/SRAdb/inst/doc/SRAdb.pdf
# This is to download/update the SRADB -- should probably do this periodically
sqlfile <- 'SRAmetadb.sqlite'
if(!file.exists('SRAmetadb.sqlite')) sqlfile <<- getSRAdbFile(destdir = "~/Documents/MountPoints/mountIDEEL/Seq_Reads/")
sra_con <- dbConnect(SQLite(),sqlfile)


sraConvert(in_acc = c("ERS032049"), out_type = c("sra"), sra_con = sra_con)

```

